------------------------------------------------------------------------

---
title: "Car Types"
author: "Erick Borda"
date: "2023-10-10"
output: pdf_document
---

# CarType Dataset Analysis Project

The goal of this analysis is to use statistical techniques on the "CarType" dataset to gain new insights and data understanding. The "CarType" dataset will be analyze with **#R**. Addressing specific business inquiries: identifying the most fuel-efficient car type and determining the most environmentally friendly car. Elaboration on particular tasks is outlined below, encompassing a concise project overview, the identified problem, the approach taken, and the major discoveries

## 1. Identified Problem

The primary problem is to identify the car type that offers the highest fuel efficiency and to determine the most environmentally friendly car based on the given dataset. This involves analyzing relevant features and variables that influence fuel efficiency and environmental impact.

## 2. Research Question

In this project, we will have a dual focus:

1.  Fuel Economy (FE) - Our research will center on optimizing fuel efficiency in various driving conditions.

2.  CO2 Emission - We will examine vehicle emissions, specifically focusing on reducing carbon dioxide (CO2) emissions.

Additionally, we will place a distinct emphasis on the **Urban sector**, delving into the unique challenges and opportunities it presents for both fuel economy and emissions analysis

### 2.1. What type of car provides the most fuel economy?

Based on the question the Null Hypothesis is:

**H0:** There is no difference in City FE between vehicles with different Cylinders, Engine Displacement and Division.

**H1:** There is difference in City FE between vehicles with different Cylinders, Engine Displacement and Division.

### 2.2. What type of car provides the most fuel economy?

Based on the question the Null Hypothesis is:

**H0:** There is no difference in City CO2 between vehicles with different Cylinders, Gears, Engine Displacement and Division.

**H1:** There is difference in City CO2 between vehicles with different Cylinders, Gears, Engine Displacement and Division.

## 3. Data Cleaning.

In the initial phase, it is essential to identify all the libraries that will be used in this project.

### 3.1. Importing Libraries.

```{r warning=FALSE}

# Install Libraries
## Excel files handling
install.packages("readxl")
## Install plot
install.packages("ggplot2")
## Install or correlation analysis
install.packages("psych")
install.packages("pheatmap")
## Install library for data manipulation and transformation 
install.packages("magrittr")
install.packages("dplyr")
# Skewness analysis
install.packages("e1071")

# Loading libraries into the session
library(readxl)
library(ggplot2)
library(psych)
library(pheatmap)
library(magrittr) 
library(dplyr)
library("e1071")
```

**Loading Excel files**, First step is setting the path:

```{r }
cartype <- read_excel("E:/Proyectos/R projects/data-projects/car-type/cartype.xls")
View(cartype)
```

### 3.2. Missing data

```{r}
# Check for missing data
missing_values <- is.na(cartype)

# Summarize missing values by column
View(summary(missing_values))
```

### 3.3. Duplicate data.

**Identified the duplicated data**, by using the following code:

```{r}
# Check for duplicate data
duplicates <- duplicated(cartype)
# Summarize duplicate data
print(sum(duplicates))
```

**Remove duplicate data**, executing the following code:

```{r}
# Remove duplicate rows using duplicated()
df_no_duplicates <- cartype[!duplicated(cartype), ]

```

## 4. Data Exploration.

### 4.1. Exploration for Numerical Data.

Descriptive statistics of all numeric data-fields:

```{r}
summary(df_no_duplicates)
```

### 4.2. Categorical Data.

Descriptive statistics of all categorical data-fields:

A method that get descriptive statistcs for categorical data with a bar graph is show below:

```{r}
calculate_categorical_stats <- function(data, col) {
  if (!is.data.frame(data)) {
    stop("Input 'data' must be a data frame.")
  }

  if (!is.vector(col)) {
    stop("Input 'col' must be a vector representing a column.")
  }

  stats <- NULL
  ggplot_obj <- NULL

  if (is.factor(col) || is.character(col)) {
    unique_values <- table(col)
    percentage_distribution <- prop.table(unique_values) * 100
    stats <- data.frame(
      Value = as.character(names(unique_values)),
      Frequency = as.numeric(unique_values),
      Percentage = as.numeric(percentage_distribution)
    )

    # Create a ggplot object for bar plot
    ggplot_obj <- ggplot(stats, aes(x = Value, y = Frequency)) +
      geom_bar(stat = "identity") +
      labs(
        title = "Frequency of the column",
        x = "Value",
        y = "Frequency"
      )
  } else if (is.numeric(col)) {
    unique_values <- table(col)
    if (length(unique_values) <= 10) {
      percentage_distribution <- prop.table(unique_values) * 100
      stats <- data.frame(
        Value = as.numeric(names(unique_values)),
        Frequency = as.numeric(unique_values),
        Percentage = as.numeric(percentage_distribution)
      )

      ggplot_obj <- ggplot(stats, aes(x = Value, y = Frequency)) +
      geom_bar(stat = "identity") +
      labs(
        title = "Frequency of the column",
        x = "Value",
        y = "Frequency"
      ) 
    }
  } else {
    stop("Column type not supported.")
  }

  result <- list(stats = stats, ggplot = ggplot_obj)
  return(result)
}
```

#### 4.2.1. Number of Cylinders

```{r}

calculate_categorical_stats(df_no_duplicates, df_no_duplicates$`# Cylinders`)

```

#### 4.2.2. Engine Displacement

```{r}

calculate_categorical_stats(df_no_duplicates, df_no_duplicates$`Engine Displacement`)

```

#### 4.2.3. Division

```{r}

calculate_categorical_stats(df_no_duplicates, df_no_duplicates$Division)

```

### 4.3. Outliers.

Only the datafields related to Fuel economy and CO2 will be evaluated due to the research question

#### 4.3.1. Fuel Economy.

```{r}
outliers <-boxplot(df_no_duplicates$`City FE`, data = df_no_duplicates,xlab="City FE")$out
print("-> City FE")
print(outliers)
outliers <-boxplot(df_no_duplicates$`Highway FE`, data = df_no_duplicates,xlab="Highway FE")$out
print("-> Highway FE")
print(outliers)
outliers <-boxplot(df_no_duplicates$`Combined FE`, data = df_no_duplicates,xlab="Combined FE")$out
print("-> Combined FE")
print(outliers)
```

#### 4.3.2. CO2 Emission.

```{r}
outliers <-boxplot(df_no_duplicates$`City CO2`, data = df_no_duplicates,xlab="City CO2")$out
print("-> City CO2")
print(outliers)
outliers <-boxplot(df_no_duplicates$`Highway CO2`, data = df_no_duplicates,xlab="Highway CO2")$out
print("-> Highway CO2")
print(outliers)
outliers <-boxplot(df_no_duplicates$`Combined CO2`, data = df_no_duplicates,xlab="Combined CO2")$out
print("-> Combined CO2")
print(outliers)
```

The decision to retain the outliers discovered in the dataset, is because these values may yield valuable insights into our analysis of car types. To gain a more comprehensive understanding of the dataset, it is essential to conduct both normal distribution to take further decisions.

### 4.4. Normal Distribution

To rigorously assess dataset normality, the following steps are employed:

-   **Data Plots:** Initial visual inspection through data plots, including histograms and Q-Q plots, serves as a preliminary assessment. Departures from a bell-shaped curve or a straight line in Q-Q plots may indicate non-normality.

-   **Skewness Test:** A skewness test quantifies data asymmetry. Positive or negative values indicate skewness. Values close to zero suggest normality.

-   **Shapiro-Wilk Test:** This formal statistical test provides a definitive verdict on normality. A p-value less than the significance level indicates non-normality.

These steps allow a conclusive determination of whether the dataset adheres to a normal distribution or deviates from it.

**Analysis for Fuel Economy:**

***City FE***

-   **Data Plots.**

```{r}

# Create the histogram
hist_data <- hist(df_no_duplicates$`City FE`, breaks = 30, plot = FALSE)    

# Plot the histogram
plot(hist_data, main = "Histogram of Sample Data",
     xlab = "City FE", ylab = "Frequency", col = "blue", border = "black")

# Create a QQ plot
qqnorm(df_no_duplicates$`City FE`, main = "QQ Plot of City FE")
qqline(df_no_duplicates$`City FE`)

```

-   **Skewness Test.**

```{r}
# Descriptive assessment
skewness_value <- e1071 ::skewness(df_no_duplicates$`Highway FE`)

if (abs(skewness_value) < 0.5) {
  description <- "approximately normally distributed"
} else if (skewness_value < -0.5) {
  description <- "left-skewed"
} else if (skewness_value > 0.5) {
  description <- "right-skewed"
} else {
  description <- "exhibiting non-normal characteristics"
}

cat("City FE data is", description, ", value: ", skewness_value)

```

-   **Shapiro-Wilk Test.**

```{r}
# Perform the Shapiro-Wilk test
shapiro_test_result <- shapiro.test(df_no_duplicates$`City FE`)

# Descriptive assessment based on the Shapiro-Wilk test result
if (shapiro_test_result$p.value > 0.05) {
  description <- "normally distributed"
} else {
  description <- "non-normal distributed"
}

cat("City FE data is", description, " p-value: ", shapiro_test_result$p.value)
```

***Highway FE***

-   **Data Plots.**

```{r}

# Create the histogram
hist_data <- hist(df_no_duplicates$`Highway FE`, breaks = 30, plot = FALSE)    

# Plot the histogram
plot(hist_data, main = "Histogram of Sample Data",
     xlab = "Highway FE", ylab = "Frequency", col = "blue", border = "black")

# Create a QQ plot
qqnorm(df_no_duplicates$`Highway FE`, main = "QQ Plot of Highway FE")
qqline(df_no_duplicates$`Highway FE`)

```

-   **Skewness Test.**

```{r}
# Descriptive assessment
skewness_value <- e1071 ::skewness(df_no_duplicates$`Highway FE`)

if (abs(skewness_value) < 0.5) {
  description <- "approximately normally distributed"
} else if (skewness_value < -0.5) {
  description <- "left-skewed"
} else if (skewness_value > 0.5) {
  description <- "right-skewed"
} else {
  description <- "exhibiting non-normal characteristics"
}

cat("Highway FE data is", description, ", value: ", skewness_value)

```

-   **Shapiro-Wilk Test.**

```{r}
# Perform the Shapiro-Wilk test
shapiro_test_result <- shapiro.test(df_no_duplicates$`Highway FE`)

# Descriptive assessment based on the Shapiro-Wilk test result
if (shapiro_test_result$p.value > 0.05) {
  description <- "normally distributed"
} else {
  description <- "non-normal distributed"
}

cat("Highway FE data is", description, " p-value: ", shapiro_test_result$p.value)
```

***Combined FE***

-   **Data Plots.**

```{r}

# Create the histogram
hist_data <- hist(df_no_duplicates$`Combined FE`, breaks = 30, plot = FALSE)    

# Plot the histogram
plot(hist_data, main = "Histogram of Sample Data",
     xlab = "Combined FE", ylab = "Frequency", col = "blue", border = "black")

# Create a QQ plot
qqnorm(df_no_duplicates$`Combined FE`, main = "QQ Plot of Combined FE")
qqline(df_no_duplicates$`Combined FE`)

```

-   **Skewness Test.**

```{r}
# Descriptive assessment
skewness_value <- e1071 ::skewness(df_no_duplicates$`Combined FE`)

if (abs(skewness_value) < 0.5) {
  description <- "approximately normally distributed"
} else if (skewness_value < -0.5) {
  description <- "left-skewed"
} else if (skewness_value > 0.5) {
  description <- "right-skewed"
} else {
  description <- "exhibiting non-normal characteristics"
}

cat("Combined FE data is", description, ", value: ", skewness_value)

```

-   **Shapiro-Wilk Test.**

```{r}
# Perform the Shapiro-Wilk test
shapiro_test_result <- shapiro.test(df_no_duplicates$`Combined FE`)

# Descriptive assessment based on the Shapiro-Wilk test result
if (shapiro_test_result$p.value > 0.05) {
  description <- "normally distributed"
} else {
  description <- "non-normal distributed"
}

cat("Combined FE data is", description, " p-value: ", shapiro_test_result$p.value)
```

The results are:

-   City FE, non-normal distributed.
-   Highway FE, non-normal distributed.
-   Combined FE, non-normal distributed.

**Analysis for CO2:**

***City CO2***

-   **Data Plots.**

```{r}

# Create the histogram
hist_data <- hist(df_no_duplicates$`City CO2`, breaks = 30, plot = FALSE)    

# Plot the histogram
plot(hist_data, main = "Histogram of Sample Data",
     xlab = "City CO2", ylab = "Frequency", col = "blue", border = "black")

# Create a QQ plot
qqnorm(df_no_duplicates$`City CO2`, main = "QQ Plot of City CO2")
qqline(df_no_duplicates$`City CO2`)

```

-   **Skewness Test.**

```{r}
# Descriptive assessment
skewness_value <- e1071 ::skewness(df_no_duplicates$`City CO2`)

if (abs(skewness_value) < 0.5) {
  description <- "approximately normally distributed"
} else if (skewness_value < -0.5) {
  description <- "left-skewed"
} else if (skewness_value > 0.5) {
  description <- "right-skewed"
} else {
  description <- "exhibiting non-normal characteristics"
}

cat("City CO2 data is", description, ", value: ", skewness_value)

```

-   **Shapiro-Wilk Test.**

```{r}
# Perform the Shapiro-Wilk test
shapiro_test_result <- shapiro.test(df_no_duplicates$`City CO2`)

# Descriptive assessment based on the Shapiro-Wilk test result
if (shapiro_test_result$p.value > 0.05) {
  description <- "normally distributed"
} else {
  description <- "non-normal distributed"
}

cat("City CO2 data is", description, " value: ", shapiro_test_result$p.value)
```

***Highway CO2***

-   **Data Plots.**

```{r}

# Create the histogram
hist_data <- hist(df_no_duplicates$`Highway CO2`, breaks = 30, plot = FALSE)    

# Plot the histogram
plot(hist_data, main = "Histogram of Sample Data",
     xlab = "Highway CO2", ylab = "Frequency", col = "blue", border = "black")

# Create a QQ plot
qqnorm(df_no_duplicates$`Highway CO2`, main = "QQ Plot of Highway CO2")
qqline(df_no_duplicates$`Highway CO2`)

```

-   **Skewness Test.**

```{r}
# Descriptive assessment
skewness_value <- e1071 ::skewness(df_no_duplicates$`Highway CO2`)

if (abs(skewness_value) < 0.5) {
  description <- "approximately normally distributed"
} else if (skewness_value < -0.5) {
  description <- "left-skewed"
} else if (skewness_value > 0.5) {
  description <- "right-skewed"
} else {
  description <- "exhibiting non-normal characteristics"
}

cat("Highway CO2 data is", description, ", value: ", skewness_value)

```

-   **Shapiro-Wilk Test.**

```{r}
# Perform the Shapiro-Wilk test
shapiro_test_result <- shapiro.test(df_no_duplicates$`Highway CO2`)

# Descriptive assessment based on the Shapiro-Wilk test result
if (shapiro_test_result$p.value > 0.05) {
  description <- "normally distributed"
} else {
  description <- "non-normal distributed"
}

cat("Highway CO2 data is", description, " value: ", shapiro_test_result$p.value)
```

*Combined CO2*

-   **Data Plots.**

```{r}

# Create the histogram
hist_data <- hist(df_no_duplicates$`Combined CO2`, breaks = 30, plot = FALSE)    

# Plot the histogram
plot(hist_data, main = "Histogram of Sample Data",
     xlab = "Combined CO2", ylab = "Frequency", col = "blue", border = "black")

# Create a QQ plot
qqnorm(df_no_duplicates$`Combined CO2`, main = "QQ Plot of Combined CO2")
qqline(df_no_duplicates$`Combined CO2`)

```

-   **Skewness Test.**

```{r}
# Descriptive assessment
skewness_value <- e1071 ::skewness(df_no_duplicates$`Combined CO2`)

if (abs(skewness_value) < 0.5) {
  description <- "approximately normally distributed"
} else if (skewness_value < -0.5) {
  description <- "left-skewed"
} else if (skewness_value > 0.5) {
  description <- "right-skewed"
} else {
  description <- "exhibiting non-normal characteristics"
}

cat("Combined CO2 data is", description, ", value: ", skewness_value)

```

-   **Shapiro-Wilk Test.**

```{r}
# Perform the Shapiro-Wilk test
shapiro_test_result <- shapiro.test(df_no_duplicates$`Combined CO2`)

# Descriptive assessment based on the Shapiro-Wilk test result
if (shapiro_test_result$p.value > 0.05) {
  description <- "normally distributed"
} else {
  description <- "non-normal distributed"
}

cat("Combined CO2 data is", description, " value: ", shapiro_test_result$p.value)
```

The results are:

-   City CO2, non-normal distributed.
-   Highway CO2, non-normal distributed.
-   Combined CO2, non-normal distributed.

### 4.5. Feature Selection.

Feature selection is a crucial step in data analysis, especially when dealing with similar data fields or variables that may have strong correlations. Its purpose is to identify and choose the most relevant and informative variables while discarding redundant or less important ones by using a correlation analysis.

**Correlation Analysis.** Due to the data is not normal distributed **Nonparametric test** should be perform

**Fuel Economy**

```{r}

data <- data.frame(
  CityFE = df_no_duplicates$`City FE`,
  HighwayFE = df_no_duplicates$`Highway FE`,
  CombinedFE = df_no_duplicates$`Combined FE`
)

# Calculate Spearman correlation matrix
correlation_matrix <- cor(data, method = "spearman")

# Print the correlation matrix
print(correlation_matrix)

# Create a heatmap
pheatmap(correlation_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(100), 
         scale = "none")
```

**CO2**

```{r}

data <- data.frame(
  CityCO2 = df_no_duplicates$`City CO2`,
  HighwayCO2 = df_no_duplicates$`Highway CO2`,
  CombinedCO2 = df_no_duplicates$`Combined CO2`
)

# Calculate Spearman correlation matrix
correlation_matrix <- cor(data, method = "spearman")

# Print the correlation matrix
print(correlation_matrix)

# Create a heatmap
pheatmap(correlation_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(100), 
         scale = "none")
```

As evident from the preceding images, the Spearman correlation test was selected. Spearman Rank Correlation (Spearman's rho) is a statistical method suitable for assessing relationships in non-normally distributed, non-linear, and ordinal data by capturing monotonic associations through the use of ranked data.

Based on the correlation results, we observe that the relationships between these three datafields are closely aligned. Additionally, considering my specific focus on urban areas, I can confidently select **City FE** as the most pertinent variable for my analysis. This choice is substantiated by the similarity in correlations and aligns with the urban-centric nature of my research.

### 4.6. Correlations: Insights & Implications.

**Fuel Economy**

```{r}

# Convert categorical to ranks
ranks_cy <- rank(df_no_duplicates$`# Cylinders`)
ranks_ed <- rank(df_no_duplicates$`Engine Displacement`)
ranks_di <- rank(df_no_duplicates$Division)

data <- data.frame(
  CityFE = df_no_duplicates$`City FE`,
  Cylinders = ranks_cy,
  EgineDisplacement = ranks_ed,
  Division = ranks_di
)

# Calculate Spearman correlation matrix
correlation_matrix <- cor(data, method = "spearman")

# Print the correlation matrix
print(correlation_matrix)

# Create a heatmap
pheatmap(correlation_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(100), 
         scale = "none")


```

**CO2 Emission**

```{r}

# Convert categorical to ranks
ranks_cy <- rank(df_no_duplicates$`# Cylinders`)
ranks_ed <- rank(df_no_duplicates$`Engine Displacement`)
ranks_di <- rank(df_no_duplicates$Division)

data <- data.frame(
  CityCO2 = df_no_duplicates$`City CO2`,
  Cylinders = ranks_cy,
  EgineDisplacement = ranks_ed,
  Division = ranks_di
)

# Calculate Spearman correlation matrix
correlation_matrix <- cor(data, method = "spearman")

# Print the correlation matrix
print(correlation_matrix)

# Create a heatmap
pheatmap(correlation_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(100), 
         scale = "none")


```

The results presented above indicate that there is a statistically significant correlation between City FE variable and the three independent variables (Number of Cylinders, Engine Displacement , Division). To further explain this relationship:

-   There is a strong negative correlation between City Fuel Economy (FE) and Engine Displacement, Number of Cylinders.

-   A weak negative correlation exists between City Fuel Economy and Division.

-   There is a strong positive correlation between City CO2 and Number of Cylinders, and Engine Displacement.

-   A weak positive correlation is observed between City Fuel Economy and Number of Gears.

### 4.7. Visual Insights into Fuel Economy and CO2.

#### 4.7.1. Fuel Economy.

**Number of Cylinders**

```{r}
boxplot(df_no_duplicates$`City FE` ~ df_no_duplicates$`# Cylinders`, data = df_no_duplicates,xlab="# Cylinders", ylab="City FE")
```

**Engine Displacement**

```{r}
boxplot(df_no_duplicates$`City FE` ~ df_no_duplicates$`Engine Displacement`, data = df_no_duplicates,xlab="Engine Displacement", ylab="City FE")
```

**Division**

```{r}
boxplot(df_no_duplicates$`City FE` ~ df_no_duplicates$Division, data = df_no_duplicates,xlab="Division", ylab="City FE")
```

#### 4.7.2. CO2 Emission.

**Number of Cylinders**

```{r}
boxplot(df_no_duplicates$`City CO2` ~ df_no_duplicates$`# Cylinders`, data = df_no_duplicates,xlab="# Cylinders", ylab="City CO2")
```

**Engine Displacement**

```{r}
boxplot(df_no_duplicates$`Combined CO2` ~ df_no_duplicates$`Engine Displacement`, data = df_no_duplicates,xlab="Engine Displacement", ylab="City CO2")
```

**Division**

```{r}
boxplot(df_no_duplicates$`Combined CO2` ~ df_no_duplicates$Division, data = df_no_duplicates,xlab="Division", ylab="City CO2")
```

## 5. Validating Hypotheses and Addressing Research Questions.

To accept or reject the null Hypotesis stated on [2. Research Question], we need to use Kruskal-Wallis test, knowing that the does not follow normal distribution, to do that we need execute the following code:

```{r}
# Perform Kruskal-Wallis test
krustal_data <- data.frame(
  CityFE = df_no_duplicates$`City FE`,
  CityCO2 = df_no_duplicates$`City CO2`,
  Cylinders = df_no_duplicates$`# Cylinders`,
  EngineDisplacement = df_no_duplicates$`Engine Displacement`,
  Division = df_no_duplicates$Division
)

# Initialize a list to store the results
kruskal_results <- list()

# Loop through combinations of numeric and categorical variables
for (numeric_var in c("CityFE", "CityCO2")) {
  for (category_var in c("Cylinders", "EngineDisplacement", "Division")) {
    formula <- paste(numeric_var, "~", category_var)
    result <- kruskal.test(as.formula(formula), data = krustal_data)
    
    # Store the results in the list
    result_name <- paste(numeric_var, "vs", category_var)
    kruskal_results[[result_name]] <- result
  }
}

# View the results
print(kruskal_results)

```

The result is p-values less than 2.2e-16 is a very strong indication that there is a significant effect or difference in your data, and you can confidently reject the null hypothesis in favor of the alternative hypothesis.

| Fuel Economy                                                                                                           | CO2 Emission                                                                                                                   | Results      |
|------------------------------------------------------------------------------------------------------------------------|--------------------------------------------------------------------------------------------------------------------------------|--------------|
| **H0:** There is no difference in City FE between vehicles with different Cylinders, Engine Displacement and Division. | **H0:** There is no difference in City CO2 between vehicles with different Cylinders, Gears, Engine Displacement and Division. | **REJECTED** |
| **H1:** There is difference in City FE between vehicles with different Cylinders, Engine Displacement and Division.    | **H1:** There is difference in City CO2 between vehicles with different Cylinders, Gears, Engine Displacement and Division.    | **ACCEPTED** |

From the above conclusion, we can say there is a relation between Fuel Economy and CO2 emissions, gathering all the information is possible to answer the research questions formulated in the context.

-   What type of car provides the most fuel economy?

-   What type of car is environmentally friendly?

The type of car that provides the most FE and lowest CO2 emission can be defined with the following characteristics:

-   Reducing the number of cylinders tents to decreased fuel consumption.

-   Smaller engines typically have lower fuel consumption.

-   Ford Cars are well know to build cars for the average men.

We can assert with confidence that vehicles with higher fuel economy are inherently more environmentally friendly, especially within the urban sector. Higher fuel economy signifies efficient use of fuel resources, leading to reduced emissions and a more sustainable transportation system in urban areas.

## 6. Recommendations.

To simplify data handling, it's advisable to utilize standardized values and avoid working with different units of measurement.

The code and results are inside of its folder Language, take a look. Your curiosity is the key to unlocking the wonders of our research!

For any inquiries or further details, please [contact me](mailto:erickborda96@.com).
